NumLin: Linear Types for Linear Algebra

### 2018-11-16 write-up/paper/implementation.tex
Declare Draft

Talk about how you implemented \lang\ and the general
architecture. Talk about how simple everything is, and also
about how implementing inference for fractions is.

@@

\begin{figure}[t]
\begin{center}
    \begin{tabular}{rcl}
        \alsocell[b]{l}{\highl{let Many x = x in} \\
        \highl{let Many x = Many (Many x) in <exp>} } &
        $\Rightarrow$ &
        \highl{<exp>}
    \\ \\
        \alsocell[c]{l}{\highl{let Many x = <exp> in} \\
            \highl{let Many x = Many (Many x) in <body>} \\
            \textbf{OR} \highl{let Many x = Many <exp> in <body>} \\
            \textbf{OR} \highl{(fun x : t -> <body>) <exp>}} &
        $\Rightarrow$ &
        \highl{let x = <exp> in <body>}
    \\ \\
        \alsocell[c]{l}{\highl{(* fixp = fix (f, x:t, <exp> : t') *)} \\
            \highl{let Many f = Many fixp in <body>} \\
            \textbf{OR} \highl{let f = fixp in <body>} } &
        $\Rightarrow$ &
        \highl{let rec f x = <exp> in <body>}
    \end{tabular}
\end{center}
\caption{Removing redundant re-bindings during translation to OCaml.}\label{fig:lang_optimise}
\end{figure}

>>>>

@@

\begin{figure}[t]
\begin{center}
    \begin{tabular}{rcl}
        \alsocell[b]{l}{\highl{let Many x = x in} \\
        \highl{let Many x = Many (Many x) in <exp>} } &
        $\Rightarrow$ &
        \highl{<exp>}
    \\ \\
        \alsocell[c]{l}{\highl{(* fixp = fix (f, x:t, <exp> : t') *)} \\
            \highl{(*1*) let Many f = Many fixp in <body>} \\
            \highl{(*2*) let f = fixp in <body>} } &
        $\Rightarrow$ &
        \highl{let rec f x = <exp> in <body>}
    \\ \\
    \alsocell[c]{l}{\highl{(*1*) let Many x = <exp> in} \\
            \highl{(*-*) let Many x = Many (Many x) in <body>} \\
            \highl{(*2*) let Many x = Many <exp> in <body>} \\
            \highl{(*3*) (fun x : t -> <body>) <exp>}} &
        $\Rightarrow$ &
        \highl{let x = <exp> in <body>}
    \end{tabular}
\end{center}
\caption{Removing redundant re-bindings during translation to OCaml.}\label{fig:lang_optimise}
\end{figure}
